MS Technical Paper: \\ Placement Algorithms for Heterogeneous FPGAs

### 2025-04-21 latex/paper/paper.tex
more dsp casc

@@

    \subsection{7-Series BEL Library}

@@

        {
            \centering
            \includegraphics[width=\columnwidth]{figures/lut_synthesis.png}
            \captionof{figure}{LUT synthesis from user design}
            \label{fig:lut_synthesis}
        }

@@

@@

        {
            \centering
            \includegraphics[width=\columnwidth]{figures/dsp_diagram.png}
            \captionof{figure}{
                Basic DSP48E1 Slice Functionality
            }
            \label{dsp_diagram}
        }

@@

        {
            \centering
            \includegraphics[valign=c, width=3.0cm]{figures/dsp_cascade_placement.png}
            \includegraphics[valign=c, width=4.0cm]{figures/dsp_cascade_routed.png}
            \captionof{figure}{
                A DSP48E1 cascade of size 2 placed across 2 DSP48E1 Sites.
                \textbf{Left:} Simplified view, \textbf{Right:} As shown in the Vivado device viewer.
            }
        }

>>>>

    \newpage
    \subsection{CLB SLICEs}

@@

@@

        {
            \centering
            \includegraphics[width=\columnwidth]{figures/lut_synthesis.png}
            \captionof{figure}{LUT synthesis from user design}
            \label{fig:lut_synthesis}
        }
        \vspace{1.0cm}

@@

    \newpage
    \subsection{DSP Slices}

@@

        {
            \centering
            \includegraphics[width=\columnwidth]{figures/dsp_diagram.png}
            \captionof{figure}{
                Basic DSP48E1 Slice Functionality
            }
            \label{dsp_diagram}
        }
        \vspace{0.5cm}

@@

        \vspace{1.0cm}
        {
            \centering
            \includegraphics[valign=c, width=2.5cm]{figures/dsp_cascade_placement.png}
            \includegraphics[valign=c, width=3.0cm]{figures/dsp_cascade_routed.png}
            \captionof{figure}{
                A DSP48E1 cascade of size 2 placed across 2 DSP48E1 Sites.
                \textbf{Left:} Simplified view, \textbf{Right:} As shown in the Vivado device viewer.
            }
        }

        \end{multicols}
        {
            \centering
            \includegraphics[valign=c, width=4.0cm]{figures/mult_synthesis.png}
            \includegraphics[valign=c, width=13.0cm]{figures/dsp_synthesis.png}
            \captionof{figure}{
                Simple multiplier synthesis from user design.
            }
            \label{mult_synthesis}
        }
        \begin{multicols}{2}
